\prefacesection{Acknowledgments}
I have enjoyed an incredible support system and academic guidance throughout my PhD.
First and foremost I must thank my primary advisor Juan Alonso, or JJ as he’s affectionately known.
The PhD experience can be highly dependent on your advisor, and he made mine very enjoyable.
His systematic approach to problem solving provided numerous research insights and taught me to do the same. 

The other reading committee members, Gianluca Iaccarino and Mykel Kochenderfer, had huge impacts on my early career as a graduate student.
Mykel was my academic advisor and helped ensure that I met all my degree requirements while teaching me to be an optimal human being. 
My early research work built upon methodologies developed by Gianluca and his guidance was instrumental in my success. 
The chair of my defense committee was Catherine Gorle, a fantastic instructor with whom I had the good fortune of taking a class. 
At my first academic conference, where I was the only one from my lab, she and her lab took me in as one of their own, showed me the ropes, and invited me to their poolside barbeque. 

The Boeing Company funded my research project
I tele-confrenced every other week with a wonderful team of people for three years.
Andrew Cary provided practical industrial experience which was instrumental in improving the quality and applicability of my research. 
Under Brian Whitehead's direction, we identified deficiencies in current modeling capabilities and created a plan to improve upon them. 
The Boeing contact I worked most closely with was Jack Quindlen.
He was always available when I needed to discuss research matters and devoted a lot of time and effort towards supporting this project.

My colleagues in the Aerospace Design Lab made me want to come into lab every day. 
Whether it is drinking Nespressos on the patio, playing soccer in the evening, or flannel Fridays, we always had fun and were ready to drop anything we were doing to help a fellow lab mate.
Being an international student, my entire support system has been the friends along the way.
In particular Michelle and Vince have seen me through my best and my worst and I am fortunate to have had their support.

Finally I must thank my family. 
Words don’t do justice to how grateful I am.
My brother Shoumit and I don’t talk much but he paved the way while I simply followed in his footsteps to come to the US for my studies.
My dad, who’s superhuman work ethic and ridiculous work hours pushed me to be the best version of myself, is a constant source of inspiration.
Finally, I want to thank my mom, who is tireless in helping others.
She equipped me with the empathy and compassion that I try and approach my life with. 

I love you all, and I would not have been able to do this without you. Thank you.